Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-26 paper/ICPC19/icpc19.tex
fixed indent

where $G$ is the group of selected maintainability guidelines from BCH (e.g., Write short units of code, etc.) and $v$ is the
version of the software under evaluation. The maintenance $M$ based on the guideline $g$ for a given version of a project is computed with the following equation:

>>>>

\noindent
where $G$ is the group of selected maintainability guidelines from BCH (e.g., Write short units of code, etc.) and $v$ is the
version of the software under evaluation. The maintenance $M$ based on the guideline $g$ for a given version of a project is computed with the following equation:
